Towards a standardized evaluation of imputation routines

### 2022-03-25 Formatted/LastDiscussed.tex
Add latexdiff file

---
title: "Towards a standardized evaluation of imputation routines"
author: "Hanne Oberman and Gerko Vink"
date: "19-1-2022"
abstract: "Developing new imputation methodology has become a very active field. Unfortunately, there is no consensus on how to perform simulation studies to evaluate the properties of imputation methods. In this paper we propose a move towards a standardized evaluation of imputation methods. To demonstrate the need for standardization, we highlight a set of potential pitfalls that bring forth a chain of potential problems in the objective assessment of the performance of imputation routines. This may lead to suboptimal use of multiple imputation in practice. Additionally, we suggest a course of action for simulating and evaluating missing data problems."
bibliography: StandardizedEvaluation.bib  
output: 
  pdf_document:
    keep_tex: true
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE)
library(dplyr)
# source(here::here("R/utils.R"))
# source(here::here("R/run_sim.R"))
```

# Introduction

Imputation is a state-of-the-art technique for drawing valid conclusions from incomplete data. The technique has earned a permanent spot in research and policy making, demonstrated e.g. by the detailed manual created by the National Research Council [@little2012prevention]. Although a top-down enforcement of valid ways to handle missing data is not yet very pronounced, an increasing amount of researchers are embracing imputation techniques. After all, the principle of imputation is very intuitive.

The idea behind imputation is to impute (fill in) missing values, to obtain a valid estimate of what could have been. A popular variant is multiple imputation [@rubi76], wherein missing values are imputed multiple times. The data that are thus obtained can be analyzed by standard techniques and, in the case of multiple imputation, the analysis results can be combined into a single inference [using Rubin's rules; @rubi87]. In contrast to ad hoc methods for dealing with missing values (e.g. list-wise deletion, mean imputation, regression imputation, last observation carried forward, indicator method), multiple imputation properly takes the sources of uncertainty that are related to the missingness problem into account.

<!-- [It has been empirically demonstrated time and again that the inferences on multiply imputed data yield unbiased and confidence valid results (through Rubin's rules). But how do we know that this is the case, if we do not have access to the true but unobserved values of the missing entries? And how can we be sure that extensions to the methodology yield valid inferences too? Especially in the field of ML/AI, there are promising new imputation methods, which may yield even sharper imputations than now-standard (semi-)parametric imputation methods. That's why we use simulation studies for the evaluation of imputation routines.] -->

The quality of a solution obtained by imputation depends on the statistical properties of the incomplete data and the degree to which an imputation procedure is able to capture these properties when modeling missing values. In general it holds that modeling missing data becomes more challenging when the amount of missingness increases. However, when (strong) relations in the data are present, the observed parts can hold great predictive power for the models that estimate the missingness. In that case, (multiple) imputation would be substantially more efficient than the ubiquitous list-wise deletion.

@@

- 10% missingness: Depending on the size of the data, this percentage can be considered as a lower bound of realistic evaluation. Anything less than 10% may be of little influence on the true data inference. Performance of a missing data method should at least be acceptable for most missing data problems. 
- 25% missingness: This is a fair amount of missingness and will, depending on the observed data information, have a noticeable influence on the completed data inference. When compared to the condition with 10% missingness, the inference obtained under 25% missingness should be less certain (i.e. confidence/credibility interval width should increase), but estimates should still be properly covered and the statistical properties of the missing data method should be sound. In practice, at least to my experience in social sciences and official statistics, 25% univariate missingness can easily be considered as a realistic missingness percentage. 
- 50% missingness: Performance under 50% percent simulated missingness will most likely be impacted severely. Depending on how the missingness mechanism interacts with the simulated data, some imputation techniques may yield estimates that are under-covered such that the completed data inference should not be deemed valid anymore. If a method yields acceptable inference under 50% MAR missingness, we can determine that the statistical properties of the imputation methodology are sound.

Although I limit the focus here to ignorable non-response, the above suggested proportions are equally applicable to simulations under non-ignorable non-response.

Fifth, the used missingness mechanism should be detailed, either graphically or written as a function of the data. Often, when inducing missingness, authors remain vague about the actual missingness mechanism under investigation and, even worse, some authors only report something like

> *We generated missing data following a MAR missingness mechanism.*

This should be considered unacceptable as claims about the validity of the multiple imputation inference depends heavily on the simulated missingness mechanism.

## Step 3. Evaluate performance

It is wise to evaluate the performance of complete case analysis (aka list-wise deletion) in all simulated conditions. We know the theoretical properties of complete case analysis, which makes the technique useful as a point of departure when evaluating multiple imputation performance. 
The evaluation criteria may depend on the estimand. When descriptive statistics are the goal and when statistical inference would not be of interest, bias of the estimates would still apply, but standard errors are generally ignored. Chances are that for those who focus on descriptive statistical applications, multiple imputation would not be the mode of choice. In general, I would say that each multiple imputation routine should be evaluated on at least the following points:

- \emph{Bias:} Results should preferable be unbiased. However, the way bias is considered can greatly influence the interpretation of the results. For example, a negligible absolute bias for a parameter for which the true value is zero, would yield infinite bias when relative bias is considered. The way bias is computed should therefore be carefully chosen and described. 
- \emph{Interval width:} The way the confidence interval is calculated should be described. Wider intervals are associated with more uncertainty and the more narrow interval that is still properly covered indicates a sharper inference. However, inference from a wider interval that is properly covered is to be considered more valid when compared to a more narrow interval that is not properly covered anymore. 
- \emph{Coverage:} Coverage of a 95% interval should in theory be $\geq 95$, where a coverage of 95% would be most efficient. Under-coverage (when estimation is too liberal) may be an indication of invalid inference, while over-coverage (when estimation is too conservative) tells us that efficiency could still be gained.
- [Add RMSE 2x]

- \emph{Distributional characteristics:} In practice, the distribution of the incomplete data may differ greatly from the observed data. Under anything but the MCAR assumption, this can be expected. When evaluating imputations, the distributional shapes should be checked and diagnostic evaluations should be performed see @abayomi2008diagnostics for an detailed overview of diagnostic evaluation for multivariate imputations. When anomalies are found, and if the imputation method is valid, there should be an explanation, especially in the controlled environment of a properly executed simulation study. 
- \emph{Plausibility of the imputed values:} Plausible imputations - imputations that could be real values if they had been observed - are not a necessary condition for obtaining valid inference. However, in practice, especially when the imputer and the analyst are different persons, plausibility of imputations may be a desired property. When evaluating imputation routines, the evaluator should mention whether the routine is prone to deliver implausible values. [Add PPC]
- \emph{Convergence of the algorithm:} Most contemporary imputation techniques rely on iterative algorithms, such as the Gibbs sampler, where some algorithms are critically considered to be possibly incompatible Gibbs samplers, PIGS, @li2012imputing. The convergence of all iterative algorithms should always be considered and if non-convergence is suspected, the inference resulting from the imputations should not be considered. [Extend this part!]
- [Add PPC (Mingyang) [@nguy17], [@zhao22]]

@@

- aim
- number of simulations

@@

- model vs design based
- data types
- sample vs population (vs bootstrapping??)
- number of observations
- number of variables
- coherence between variables

@@

- monotone/univariate vs multivariate
- missingness mechanism
- type of M(N)AR
- missingness proportion

@@

- imputation method
- imputation model
- number of imputations
- number of iterations

@@

- analysis model
- estimand
- diagnostic
- ppc

# Discussion

This document is aimed at establishing a common ground for the evaluation of imputation routines. Such a common ground would be the basis of a standardized evaluation. This allows for fair and efficient comparisons between imputation techniques. Ultimately, it would be desirable to evaluate every imputation routine against the same standardized set in order to quantify the statistical properties across imputation routines. If properly executed, this would allow for careful matching of imputation methodologies to new missing data problems.

# Appendix A: Simulation setup

Let $Y=(Y_{obs},Y_{mis})$ be an incomplete semi-continuous variable, where $Y_{obs}$ and $Y_{mis}$ denote the observed values and the missing values in $Y$, respectively.  Further, $X=(X_1,...,X_k)$ is a set of $k$ fully observed covariates, where $X_{obs}$ and $X_{mis}$ correspond to the observed an missing parts in $Y$ and where $X_j$ would indicate the $j$th variable in $X$, with $j=1,\dots, k$. Finally, let $R$ be a response indicator that is 1 if $Y$ is observed and 0 if $Y$ is missing.

To prove the point, I generated a single data set from the multivariate normal distribution with means
$$
\mu= \bordermatrix{&	 \cr
 Y	&5	\cr
{ X}_1	&10	\cr
{ X}_2	&10	},
$$
and covariance matrix
$$
\Sigma = \bordermatrix{& Y &{ X}_1 &{ X}_2	 \cr
 Y	&1	&0.8	&0\cr
{ X}_1	&0.8	&1	&0\cr
{ X}_2	&0	&0	&1}.
$$

Three incomplete sets were then generated, wherein random missingness was imposed in $Y$ in three ways. First, I left the observed data \emph{observed at random} to impose MCAR missingness following the mechanism 
$$
P(R=0|Y_{obs},Y_{mis}, X_j)=P(R=0)=.50.
$$
Next, I created random missingness in $Y$ according to the following MAR missingness mechanism
$$
P(R=0|Y_{obs},Y_{mis}, X_j)=P(R=0|Y_{obs}, X_j),
$$
by using a random draw from a binomial distribution of the same length as $Y$ and of size 1 with missingness probability equal to the inverse logit
$$
P(R=0)=\frac{e^{a}}{(1+e^{a})}.
$$
where $a=(\mu_{X_j}-X_{ij})/\sqrt{\mathbb{E}[X_{ij} - \mu_{X_j}]}$ in order to create approximately 50% right-tailed MAR missingness. I followed this procedure twice; once for each $X_j$.

The three resulting incomplete data sets were then imputed with package `mice` @mice, v2.25, in `R` @R, v3.2.3, with Bayesian linear regression imputation (`mice.impute.norm`) as the imputation routine.  The completed-data analyses were combined into a single inference following the rules described in @vink2014pooling.

```{r}
sessionInfo()

```

# References

>>>>

\documentclass[bimj,fleqn]{w-art}
\usepackage{times}
\usepackage{w-thm}
\usepackage[authoryear]{natbib}
% \setlength{\bibsep}{2pt}
% \setlength{\bibhang}{2em}
% \newcommand{\J}{J\"{o}reskog}
% \newcommand{\So}{S\"{o}rbom}
% \newcommand{\bcx}{{\bf X}}
% \newcommand{\bcy}{{\bf Y}}
% \newcommand{\bcz}{{\bf Z}}
% \newcommand{\bcu}{{\bf U}}
% \newcommand{\bcv}{{\bf V}}
% \newcommand{\bcw}{{\bf W}}
% \newcommand{\bci}{{\bf I}}
% \newcommand{\bch}{{\bf H}}
% \newcommand{\bcb}{{\bf B}}
% \newcommand{\bcr}{{\bf R}}
% \newcommand{\bcm}{{\bf M}}
% \newcommand{\bcf}{{\bf F}}
% \newcommand{\bcg}{{\bf G}}
% \newcommand{\bcs}{{\bf S}}
% \newcommand{\bca}{{\bf A}}
% \newcommand{\bcd}{{\bf D}}
% \newcommand{\bcc}{{\bf C}}
% \newcommand{\bce}{{\bf E}}
% \newcommand{\ba}{{\bf a}}
% \newcommand{\bb}{{\bf b}}
% \newcommand{\bc}{{\bf c}}
% \newcommand{\bd}{{\bf d}}
% \newcommand{\bx}{{\bf x}}
% \newcommand{\by}{{\bf y}}
% \newcommand{\bz}{{\bf z}}
% \newcommand{\bu}{{\bf u}}
% \newcommand{\bv}{{\bf v}}
% \newcommand{\bh}{{\bf h}}
% \newcommand{\bl}{{\bf l}}
% \newcommand{\be}{{\bf e}}
% \newcommand{\br}{{\bf r}}
% \newcommand{\bw}{{\bf w}}
% \newcommand{\de}{\stackrel{D}{=}}
% \newcommand{\bt}{\bigtriangleup}
% \newcommand{\bfequiv}{\mbox{\boldmath $\equiv$}}
% \newcommand{\bmu}{\mbox{\boldmath $\mu$}}
% \newcommand{\bnu}{\mbox{\boldmath $\nu$}}
% \newcommand{\bxi}{\mbox{\boldmath $\xi$}}
% \newcommand{\btau}{\mbox{\boldmath $\tau$}}
% \newcommand{\bgamma}{\mbox{\boldmath $\Gamma$}}
% \newcommand{\bphi}{\mbox{\boldmath $\Phi$}}
% \newcommand{\bfphi}{\mbox{\boldmath $\varphi$}}
% \newcommand{\bfeta}{\mbox{\boldmath $\eta$}}
% \newcommand{\bpi}{\mbox{\boldmath $\Pi$}}
% \newcommand{\bequiv}{\mbox{\boldmath $\equiv$}}
% \newcommand{\bvarepsilon}{\mbox{\boldmath $\varepsilon$}}
% \newcommand{\btriangle}{\mbox{\boldmath $\triangle$}}
% \newcommand{\bdelta}{\mbox{\boldmath $\Delta$}}
% \newcommand{\beps}{\mbox{\boldmath $\epsilon$}}
% \newcommand{\btheta}{\mbox{\boldmath $\theta$}}
% \newcommand{\balpha}{\mbox{\boldmath $\alpha$}}
% \newcommand{\bsphi}{\mbox{\boldmath $\varphi$}}
% \newcommand{\bsig}{\mbox{\boldmath $\sigma$}}
% \newcommand{\bfpsi}{\mbox{\boldmath $\psi$}}
% \newcommand{\bfdelta}{\mbox{\boldmath $\delta$}}
% \newcommand{\bsigma}{{\bf \Sigma}}
% \newcommand{\bzero}{{\bf 0}}
% \newcommand{\bpsi}{\mbox{\boldmath $\Psi$}}
% \newcommand{\bep}{\mbox{\boldmath $\epsilon$}}
% \newcommand{\bomega}{\mbox{\boldmath $\Omega$}}
% \newcommand{\bfomega}{\mbox{\boldmath $\omega$}}
% \newcommand{\blambda}{\mbox{\boldmath $\Lambda$}}
% \newcommand{\bflambda}{\mbox{\boldmath $\lambda$}}
% \newcommand{\bfsigma}{\mbox{\boldmath $\sigma$}}
% \newcommand{\bfpi}{{\mbox{\boldmath $\pi$}}}
% \newcommand{\bupsilon}{\mbox{\boldmath $\upsilon$}}
% \newcommand{\obs}{{\rm obs}}
% \newcommand{\mis}{{\rm mis}}
% \theoremstyle{plain}
% \newtheorem{criterion}{Criterion}
% \theoremstyle{definition}
% \newtheorem{condition}[theorem]{Condition}
% \usepackage[]{graphicx}
% \chardef\bslash=`\\ % p. 424, TeXbook
% \newcommand{\ntt}{\normalfont\ttfamily}
% \newcommand{\cn}[1]{{\protect\ntt\bslash#1}}
% \newcommand{\pkg}[1]{{\protect\ntt#1}}
% \let\fn\pkg
% \let\env\pkg
% \let\opt\pkg
% \hfuzz1pc % Don't bother to report overfull boxes if overage is < 1pc
% \newcommand{\envert}[1]{\left\lvert#1\right\rvert}
% \let\abs=\envert

\begin{document}
%\DOIsuffix{bimj.DOIsuffix}
\DOIsuffix{bimj.200100000}
\Volume{52}
\Issue{61}
\Year{2010}
\pagespan{1}{}
\keywords{Evaluation; Imputation; Missing data; Simulation studies;\\[1pc]
\noindent \hspace*{-4.2pc} Supporting Information for this article is available from Github, \break \hspace*{-4pc} \underline{github.com/gerkovink/StandardizedEvaluation}.
}  %%% semicolon and fullpoint added here for keyword style

\title[Standardized evaluation]{Towards a standardized evaluation of imputation routines}
%% Information for the first author.
\author[Oberman]{Hanne I. Oberman\footnote{Corresponding author: {\sf{e-mail: h.i.oberman@uu.nl}}}\inst{,1}} 
\address[\inst{1}]{Departement of Methodology \& Statistics, Padualaan 14, 3584 CH Utrecht, The Netherlands}
%%%%    Information for the second author
\author[Vink]{Gerko Vink\inst{1}}
%%%%    \dedicatory{This is a dedicatory.}
\Receiveddate{zzz} \Reviseddate{zzz} \Accepteddate{zzz}

\begin{abstract}
Developing new imputation methodology has become a very active field. Unfortunately, there is no consensus on how to perform simulation studies to evaluate the properties of imputation methods. In this paper we propose a move towards a standardized evaluation of imputation methods. To demonstrate the need for standardization, we highlight a set of potential pitfalls that bring forth a chain of potential problems in the objective assessment of the performance of imputation routines. This may lead to suboptimal use of multiple imputation in practice. Additionally, we suggest a course of action for simulating and evaluating missing data problems.
\end{abstract}

%% maketitle must follow the abstract.
\maketitle                   % Produces the title.

%% If there is not enough space inside the running head
%% for all authors including the title you may provide
%% the leftmark in one of the following three forms:

%% \renewcommand{\leftmark}
%% {First Author: A Short Title}

%% \renewcommand{\leftmark}
%% {First Author and Second Author: A Short Title}

%% \renewcommand{\leftmark}
%% {First Author et al.: A Short Title}

%% \tableofcontents  % Produces the table of contents.

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Imputation is a state-of-the-art technique for drawing valid conclusions from incomplete data. The technique has earned a permanent spot in research and policy making, demonstrated e.g. by the detailed manual created by the National Research Council \citep*{little2012prevention}. Although a top-down enforcement of valid ways to handle missing data is not yet very pronounced, an increasing amount of researchers are embracing imputation techniques. After all, the principle of imputation is very intuitive.

The idea behind imputation is to impute (fill in) missing values, to obtain a valid estimate of what could have been. A popular variant is multiple imputation \citep{rubi76}, wherein missing values are imputed multiple times. The data that are thus obtained can be analyzed by standard techniques and, in the case of multiple imputation, the analysis results can be combined into a single inference \citep[using Rubin's rules][]{rubi87}. In contrast to ad hoc methods for dealing with missing values (e.g. list-wise deletion, mean imputation, regression imputation, last observation carried forward, indicator method), multiple imputation properly takes the sources of uncertainty that are related to the missingness problem into account.

The quality of a solution obtained by imputation depends on the statistical properties of the incomplete data and the degree to which an imputation procedure is able to capture these properties when modeling missing values. In general it holds that modeling missing data becomes more challenging when the amount of missingness increases. However, when (strong) relations in the data are present, the observed parts can hold great predictive power for the models that estimate the missingness. In that case,  imputation would be substantially more efficient than the ubiquitous list-wise deletion.

@@

\begin{itemize}
  \item 10\% missingness: Depending on the size of the data, this percentage can be considered as a lower bound of realistic evaluation. Anything less than 10\% may be of little influence on the true data inference. Performance of a missing data method should at least be acceptable for most missing data problems. 
  \item 25\% missingness: This is a fair amount of missingness and will, depending on the observed data information, have a noticeable influence on the completed data inference. When compared to the condition with 10\% missingness, the inference obtained under 25\% missingness should be less certain (i.e. confidence/credibility interval width should increase), but estimates should still be properly covered and the statistical properties of the missing data method should be sound. In practice, at least to my experience in social sciences and official statistics, 25\% univariate missingness can easily be considered as a realistic missingness percentage. 
  \item 50\% missingness: Performance under 50\% percent simulated missingness will most likely be impacted severely. Depending on how the missingness mechanism interacts with the simulated data, some imputation techniques may yield estimates that are under-covered such that the completed data inference should not be deemed valid anymore. If a method yields acceptable inference under 50\% MAR missingness, we can determine that the statistical properties of the imputation methodology are sound. 
\end{itemize}
Although I limit the focus here to ignorable non-response, the above suggested proportions are equally applicable to simulations under non-ignorable non-response.

Fifth, the used missingness mechanism should be detailed, either graphically or written as a function of the data. Often, when inducing missingness, authors remain vague about the actual missingness mechanism under investigation and, even worse, some authors only report something like
\begin{quote}
\emph{We generated missing data following a MAR missingness mechanism.}
\end{quote}
This should be considered unacceptable as claims about the validity of the multiple imputation inference depends heavily on the simulated missingness mechanism.

%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Step 3. Evaluate performance}

It is wise to evaluate the performance of complete case analysis (aka list-wise deletion) in all simulated conditions. We know the theoretical properties of complete case analysis, which makes the technique useful as a point of departure when evaluating multiple imputation performance. 
The evaluation criteria may depend on the estimand. When descriptive statistics are the goal and when statistical inference would not be of interest, bias of the estimates would still apply, but standard errors are generally ignored. Chances are that for those who focus on descriptive statistical applications, multiple imputation would not be the mode of choice. In general, we would say that each multiple imputation routine should be evaluated on at least the following points:
\begin{itemize}
  \item \emph{Bias:} Results should preferable be unbiased. However, the way bias is considered can greatly influence the interpretation of the results. For example, a negligible absolute bias for a parameter for which the true value is zero, would yield infinite bias when relative bias is considered. The way bias is computed should therefore be carefully chosen and described. 
  \item \emph{Interval width:} The way the confidence interval is calculated should be described. Wider intervals are associated with more uncertainty and the more narrow interval that is still properly covered indicates a sharper inference. However, inference from a wider interval that is properly covered is to be considered more valid when compared to a more narrow interval that is not properly covered anymore. 
  \item \emph{Coverage:} Coverage of a 95\% interval should in theory be $\geq 95$, where a coverage of 95\% would be most efficient. Under-coverage (when estimation is too liberal) may be an indication of invalid inference, while over-coverage (when estimation is too conservative) tells us that efficiency could still be gained. 
  \item \emph{RMSE:} [RMSE at cell level and at prediction level (if applicable).]
  \item \emph{Distributional characteristics:} In practice, the distribution of the incomplete data may differ greatly from the observed data. Under anything but the MCAR assumption, this can be expected. When evaluating imputations, the distributional shapes should be checked and diagnostic evaluations should be performed \citep[see][for an detailed overview of diagnostic evaluation for multivariate imputations]{abayomi2008diagnostics}. When anomalies are found, and if the imputation method is valid, there should be an explanation, especially in the controlled environment of a properly executed simulation study. 
  \item \emph{Plausibility of the imputed values:} Plausible imputations - imputations that could be real values if they had been observed - are not a necessary condition for obtaining valid inference. However, in practice, especially when the imputer and the analyst are different persons, plausibility of imputations may be a desired property. When evaluating imputation routines, the evaluator should mention whether the routine is prone to deliver implausible values. 
  \item \emph{Fit of the imputation model:} [PPC, ref Mingyang, \citep{nguy17, zhao22}.]
  \item \emph{Convergence of the algorithm:} Most contemporary imputation techniques rely on iterative algorithms, such as the Gibbs sampler, where some algorithms are critically considered to be possibly incompatible Gibbs samplers \citep[PIGS,][]{li2012imputing}. The convergence of all iterative algorithms should always be considered and if non-convergence is suspected, the inference resulting from the imputations should not be considered.  
  \end{itemize}

@@

- aim

- number of simulations

@@

- model vs design based

- data types

- sample vs population (vs bootstrapping??)

- number of observations

- number of variables

- coherence between variables

@@

- monotone/univariate vs multivariate

- missingness mechanism

- type of M(N)AR

- missingness proportion

@@

- imputation method

- imputation model

- number of imputations

- number of iterations

@@

- analysis model

- estimand

- diagnostic

- ppc

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% DISCUSSION
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{acknowledgement}
[Maybe add Gelman here?]
\end{acknowledgement}
\vspace*{1pc}

\noindent {\bf{Conflict of Interest}}

\noindent {\it{The authors have declared no conflict of interest. (or please state any conflicts of interest)}}

% \section*{Appendix {\it(please insert here, if applicable)}}
% 
% \subsection*{A.1.\enspace Second level heading}
% 
% Please insert appendices before the references.

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{bibliography}
\bibliographystyle{apalike}

% \begin{thebibliography}{10}
% \bibitem[Bauer and Bauer(1994)Bauer, P. and Bauer, M.M.]{bib1}Bauer, P. and  Bauer, M. M. (1994). Testing equivalence simultaneously for location and  dispersion of two normally distributed populations.  \textit{Biometrical  Journal} \textbf{36}, 643--660.
% \bibitem[Farrington, C. P. and Andrews, N. (2003)]{bib2}Farrington, C.P. and Andrews, N. (2003). Outbreak detection:
% Application to infectious disease surveillance. In: Monitoring the Health of Populations (eds. R. Brookmeyer and D. F. Stroup), Oxford University Press, Oxford,\break 203--231.
% \bibitem[Rencher(1998)Rencher, A.C.]{bib3}Rencher, A. C. (1998).  \textit{Multivariate Statistical Inference and Applications}. Wiley, New  York. 
% \end{thebibliography}
% \newpage
% \phantom{aaaa}
\end{document}
